### 2017-02-24 robust-software.tex
Made fixups according to PLOS guidelines

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section{#1}}
\newcommand{\ruleminor}[1]{\textbf{#1}}
\begin{document}
\vspace*{0.2in}

@@

If you are new to version control, it is simplest to treat it as ``a
better \withurl{Dropbox}{http://dropbox.com}'' (or, if you are of a
certain age, a better FTP), and to use it simply to synchronize files
between multiple developers and machines~\cite{blischak2016}.  Once
you are comfortable working that way, you should \ruleminor{use a
feature branch workflow}: designate one parallel copy (or
``branch'') of the repository as the master, and create a new branch
from it each time you want to fix a bug or add a new feature.  This
allows work on independent changes to proceed in isolation; once the
work has been completed and tested, it can be merged into the master
branch for release.

@@

\withurl{Semantic versioning}{http://semver.org/} is one of the most
common types of versioning for open-source software. Version numbers
take the form of \emph{MAJOR.MINOR{[}.PATCH{]}}, e.g., 0.2.6.  Changes
in the major version number herald significant changes in the software
that are not backwards compatible, such as changing or removing
features or altering the primary functions of the software. Increasing
the minor version represents incremental improvements in the software,
like adding new features. Following the minor version number can be an
arbitrary number of project-specific identifiers, including patches,
builds and qualifiers.  Common qualifiers include \texttt{alpha},
\texttt{beta}, and \texttt{SNAPSHOT}, for applications that are not
yet stable or released, and \texttt{-RC} for release candidates prior
to an official release.

@@

>>>>

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section*{#1}}
\newcommand{\ruleminor}[1]{\textbf{#1}}
\begin{document}
\vspace*{0.2in}

@@

If you are new to version control, it is simplest to treat it as ``a
better Dropbox'' (or, if you are of a
certain age, a better FTP), and to use it simply to synchronize files
between multiple developers and machines~\cite{blischak2016}.  Once
you are comfortable working that way, you should \ruleminor{use a
feature branch workflow}: designate one parallel copy (or
``branch'') of the repository as the master, and create a new branch
from it each time you want to fix a bug or add a new feature.  This
allows work on independent changes to proceed in isolation; once the
work has been completed and tested, it can be merged into the master
branch for release.

@@

Semantic versioning~\cite{semver} is one of the most
common types of versioning for open-source software. Version numbers
take the form of \emph{MAJOR.MINOR{[}.PATCH{]}}, e.g., 0.2.6.  Changes
in the major version number herald significant changes in the software
that are not backwards compatible, such as changing or removing
features or altering the primary functions of the software. Increasing
the minor version represents incremental improvements in the software,
like adding new features. Following the minor version number can be an
arbitrary number of project-specific identifiers, including patches,
builds and qualifiers.  Common qualifiers include \texttt{alpha},
\texttt{beta}, and \texttt{SNAPSHOT}, for applications that are not
yet stable or released, and \texttt{-RC} for release candidates prior
to an official release.

@@

\section*{Supporting information}

\emph{S1 Checklist. Robust software checklist.} A checklist summarizing these ten simple rules to apply to your own
software.
